Attributes-based Object Classification and Segmentation

### 2010-05-12 trunk/paper.tex
changes

Our work focuses on leveraging attributes to produce accurate segmentations.
The idea is to find image regions with attribute distributions very similar
to some canonical distribution for an object.  We define the ``canonical distribution''
to be an attribute distribution representative of that object.  For example, the
canonical distribution for a ``car'' would have some measure of ``shininess'', some
other measure of ``window'' and so forth.  If
regions can be combined together to for larger regions with attribute
distributions matching the object's canonical distribution then one can
declare the combined region an accurate segmentation for that object.

We note that it is possible that one segmented region may contain the object and
nothing else.  Though possible, in practice it is highly unlikely.  Even for rather
simple objects, the true region of the object is distributed among various
segmentations.  This is because all but the most trivial objects have different
sub-regions of different colors, textures, contours, etc.  Thus we must search
for a combination of these sub-regions that make up the object.

@@

Object classification can give some top-down high-level information
for segmentation. On the other hand, segmentation can provide
image-based coherence information for classification. To deal with
the problem that the bottom-up single segmentation is not accurate,
more and more algorithms are based on multiple segmentations. Gu et
al \cite{gu09} uses the hierarchical segmentation algorithm to
generate multiple segments, and detect different parts of objects in
each segment. The final objects are voted for by the various parts.
We will initially be using the same segmentation algorithm used in
this paper, but without discarding the hierarchy.
Russell et al \cite{russell06} detect the whole object in each of
the multiple segment, by assuming that most objects get segmented
correctly at least once during the multiple segmentation. Our approach
will be far less aggressive in that we will use object classes and
features (attributes in our case) that are known \emph{a priori}.
Pantofaru et
al \cite{pantofaru} use three different segmentation algorithms to
generate the multiple segments. After detecting objects in each
segment, they merge the intersected segments as final results. In
our method, we use common knowledge of distribution of attributes to
merge segments.
Borenstein et al \cite{borenstein04} proposed a method of combining top-down
and bottom-up information to generate a high-quality segmentation.  Their
approach to the top-down is to use exemplar image fragments and match them
to the image and then refining the top-down segmentation using their
segmentation hierarchy.  Our approach doesn't use any confidence boosting based
on the hierarchy like they do, but rather, the hierarchy is used to guide
efficient removal and combination of regions.

@@

We use a similar algorithm to that used in \cite{farhadi09} to train the attribute models. Three different type of features are used: HOG, texture and color descriptors \cite{farhadi09}.  We use kmeans to quantize the features. The HOG descriptors are quantized into 1000 clusters, and the texture and color are quantized to 256 and 128 clusters, respectively. All quantized features are concatenated to form a 1384 dimensional feature.  These low-level features are generated for training and testing datasets using the entire image.  This is done to avoid introducing any feature artifacts as a result of black space surrounding segmented regions.

>>>>

Our work focuses on leveraging attributes to produce accurate segmentations.
The idea is to find image regions with attribute distributions very similar
to some canonical distribution for an object.  Figure \ref{fig:truck} shows
an example.  We define the ``canonical distribution''
to be an attribute distribution representative of that object.  For example, the
canonical distribution for a ``car'' would have some measure of ``shininess'', some
other measure of ``window'' and so forth.  If
regions can be combined together to for larger regions with attribute
distributions matching the object's canonical distribution then one can
declare the combined region an accurate segmentation for that object.

%We note that it is possible that one segmented region may contain the object and
%nothing else.  Though possible, in practice it is highly unlikely.  Even for rather
%simple objects, the true region of the object is distributed among various
%segmentations.  This is because all but the most trivial objects have different
%sub-regions of different colors, textures, contours, etc.  Thus we must search
%for a combination of these sub-regions that make up the object.

@@

Object classification can give some top-down high-level information
for segmentation. On the other hand, segmentation can provide
image-based coherence information for classification. To deal with
the problem that the bottom-up single segmentation is not accurate,
more and more algorithms are based on multiple segmentations. Gu et
al \cite{gu09} uses the hierarchical segmentation algorithm to
generate multiple segments, and detect different parts of objects in
each segment. The final objects are voted for by the various parts.
We will initially be using the same segmentation algorithm used in
this paper, but without discarding the hierarchy.

Russell et al \cite{russell06} attempt object classification 
by assuming that most objects get segmented
correctly at least once during the multiple segmentation. We make no such
assumption.  Rather, we find some region that contains the entire
object (which may be the original image) and refine that rough
segmentation.  Russell et all also learn object classes in an
unsupervised manner.  Our approach
will be far less aggressive in that we will use object classes 
that are known \emph{a priori}.
Pantofaru et
al \cite{pantofaru} use three different segmentation algorithms to
generate the multiple segments. After detecting objects in each
segment, they merge the intersected segments as final results. In
our method, we use common knowledge of distribution of attributes to
merge segments.
Borenstein et al \cite{borenstein04} proposed a method of combining top-down
and bottom-up information to generate a high-quality segmentation.  Their
approach to the top-down is to use exemplar image fragments and match them
to the image and then refining the top-down segmentation using their
segmentation hierarchy.  Our approach doesn't use any confidence boosting based
on the hierarchy like they do, but rather, the hierarchy is used to guide
efficient removal and combination of regions.

@@

We use a similar algorithm to that used in \cite{farhadi09} to train the attribute models. 
Three different type of features are used: HOG, texture and color descriptors \cite{farhadi09}.  
We use kmeans to quantize the features. The HOG descriptors are quantized into 1000 clusters, 
and the texture and color are quantized to 256 and 128 clusters, respectively. 
All quantized features are concatenated to form a 1384 dimensional feature.
Since all features are local, we represent a segment by using only features inside the segment
to produce a feature histogram.  In other words, rather than segmenting the image and finding features,
we find features and then segment the features.
This is done to avoid introducing any feature artifacts as a result of black space surrounding 
segmented regions in the image.
